Class differences in social networks: Evidence from a referral experiment

### 2025-06-19 writing/manuscript.tex
Revise regression models and update manuscript text
Expanded Stata regression scripts to include program and SES interactions, added new variables, and restructured model specifications for clarity. Updated manuscript.tex to clarify SES diversity analysis, referral characteristics, and regression modeling approach, including a new description and formula for the conditional logit model.

\subsection{SES diversity in networks}\label{s:ses-diversity}
What are diversity related consequences of SES-driven differences across networks? In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means. However, it is important to note that these are not independent observations for each network. Estimates are precise because each network is a draw with replacement from the same pool of university population. Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping). For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups. Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.

@@

What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network? Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students. First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}). This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties. While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses. The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers within same program (93\%).

@@

\textcolor{red}{regression time!}

>>>>

\subsection{SES diversity in networks}\label{s:ses-diversity}
What are diversity related consequences of SES-driven differences across networks? In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means. However, it is important to note that these are not independent observations for each network. Estimates are precise because each network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group. Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping). For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups. Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.

@@

What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network? Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students. First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}). This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties. While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses. The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with high social proximity and within same program (93\%).

@@

We model a single referral outcome from candidates that are mutually exclusive, where our the dependent variable outcome is multinomial distributed. Our design leverages the enrollment network to generate dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for all referral candidates, and not just the chosen alternative. Using a conditional logit model with these data, we can identify whether SES groups have an aggregate bias each other:

\begin{align*}
            \Pr(\text{Refer}_{ij} = 1) = \Lambda\left(\beta_1 \text{SES}_j + \beta_2 \text{Courses}_j + \beta_3 \text{Score}_{ij} + \beta_4 \text{Courses}_j \times \text{Score}_{ij} + \alpha_i\right)
        \end{align*}

“The income coefficients of , , and mean that, relative to the probability of beach fishing, an increase in income leads to a decrease in the probability of charter boat and pier fishing and an increase in the probability of private boat fishing”
